---
title: "p8105_hw5_ls3751"
author: "Liucheng Shi"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



```{r, error = TRUE}
city_prop_test = function(df) {
  
  n_unsovled ...
  n_total ... 
  
  prop.test(.....)
  
}


homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  nest(data = resolved)
```





## Problem 2

### 2.1 Start with a dataframe containing all file names, iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

```{r, message = F}
study_df = 
  tibble(
    path = list.files("data"),
  ) %>% 
  mutate(
    path = str_c("data/", path),
    data = map(.x = path, ~read_csv(.x)))
```

### 2.2 Tidy the result; manipulate file names to include control arm and subject ID

```{r}
study_tidy = study_df %>% 
  unnest(data) %>% 
  mutate(path = str_extract(path,"[a-z][a-z][a-z][\\_][0-9][0-9]")) %>% 
  separate(path, c("arm","id"), sep = "_") %>% 
  mutate(arm = case_when(
    arm == "con" ~ "control",
    arm == "exp" ~ "experimental"),
    id = factor(id), arm = factor(arm)) %>% 
  pivot_longer(week_1:week_8,
               names_to = "week",
               names_prefix = "week_",
               values_to = "observation") %>% 
  mutate(week = factor(week))
```

### 2.3 Make a spaghetti plot showing observations on each subject over time

```{r}
study_tidy %>% 
  ggplot(aes(x = week, y = observation, group = id, color = id)) +
  geom_line() +
  labs(
    title = "Spaghetti plot - observations over time",
    x = "Time (week)",
    y = "Observations on each subject") +
  facet_grid(. ~ arm)
```


## Problem 3 simulation to explore power in a one-sample t-test!!


### 3.1 Generate the datasets for mu = 0,1,2,3,4,5,6

```{r, cache = T}
stimulation = function(mu, sd = 5, size = 30, iterate = 5000){
  stimulation = tibble(
    mu = mu,
    trial = seq(1:iterate),
    results = rerun(iterate, rnorm(size, mu, sd)))
  stimulation_df = stimulation %>%
    mutate(ttest = map(.x = results, ~t.test(.x))) %>% 
    mutate(pvalue = map(.x = ttest, ~broom::tidy(.x))) %>% 
    unnest(pvalue) %>% 
    select(mu, trial, estimate, p.value) %>%
    mutate(sample_mean = estimate, p_value = p.value, .keep = "unused",
           decision = case_when(
             p_value < 0.05 ~ "Reject",
             p_value >= 0.05 ~ "Fail to reject"
           ))
  return(stimulation_df)
}

stimulation_combine = tibble(
  output = map(.x = 0:6, ~stimulation(.x)))

stimulation_df = stimulation_combine %>% 
  unnest(cols = c(output))
```

### 3.2 Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis

```{r, message = F}
summary_df = stimulation_df %>% 
  group_by(mu) %>% 
  summarize(percent = length(decision[decision == "Reject"])/n()) %>% 
  as_tibble()
```

```{r}
summary_df %>% 
  ggplot(aes(x = mu, y = percent)) +
  geom_point(size = 1.5) +
  geom_line() +
  labs(
    title = "The association between size effect and power",
    x = "True value of μ",
    y = "Power") 
```



